EvoSuite at the SBST 2016 Tool Competition

### 2016-02-22 papers/sbst16/paper_sbst16.tex
last pass

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2016.  Details about the competition and the benchmark
can be found in [TODO]. 
In this competition, \EVOSUITE achieved a 1126.7 overall score, which was the highest among
the competing tools.

@@

On average, \EVOSUITE generated 0.14 flaky tests per run, a value that
is significantly lower than that of any of the competing tools. This
is due to extensive efforts to isolate \EVOSUITE tests from the
execution environment~\cite{arcuri2014automated}. A few of these flaky
tests were introduced by recent changes to \EVOSUITE following
experiments on Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE
now includes assertions on the source of exceptions, similar to
commercial tools like Agitar One~\cite{agitarone}. Unfortunately,
there were several instances in the competition where these assertions
lead to flaky tests. For example, the following is an excerpt from a
test for the Defects4J bug Lang-41, generated by \EVOSUITE:

@@

%\noindent
\textbf{Acknowledgments.}

Many thanks to all the contributors to \EVOSUITE.
This project has been funded by 
%the EPSRC project ``EXOGEN'' (EP/K030353/1), a Google Focused Research Award on ``Test
%Amplification'', and by 
the National Research Fund, Luxembourg (FNR/P10/03).

>>>>

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2016.  Details about the competition and the benchmark
can be found in~\cite{sbst16competition}. 
In this competition, \EVOSUITE achieved a 1126.7 overall score, which was the highest among
the competing tools.

@@

On average, \EVOSUITE generated 0.14 flaky tests per run, a value that
is significantly lower than that of any of the competing tools. This
is due to extensive efforts to isolate \EVOSUITE tests from the
execution environment~\cite{arcuri2014automated}. A few of these flaky
tests were introduced by recent changes to \EVOSUITE following
experiments on Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE
now includes assertions on the source of exceptions, similar to
commercial tools like Agitar One. %~\cite{agitarone}. 
Unfortunately, there were several instances in the competition where these assertions
lead to flaky tests. For example, the following is an excerpt from a
test for the Defects4J bug Lang-41, generated by \EVOSUITE:

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by 
%the EPSRC project ``EXOGEN'' (EP/K030353/1), a Google Focused Research Award on ``Test
%Amplification'', and by 
the National Research Fund, Luxembourg (FNR/P10/03).
